\documentclass{beamer}
\usepackage{pgf}
\usepackage{amsmath}
\usepackage{multirow}
\usepackage{setspace}
\usepackage{threeparttable}
\usepackage[english]{babel}
\usepackage{multimedia}
\usepackage{hyperref}
\usepackage{epstopdf}
\usepackage{subfigure}
\usepackage{graphicx}
\usepackage{scalefnt}
\usepackage{tikz}
\usepackage{eepic}

\DeclareMathOperator*{\plim}{plim}

\def\independenT#1#2{\mathrel{\rlap{$#1#2$}\mkern2mu{#1#2}}}

\mode<presentation>
{
\setbeamercovered{transparent}
\usetheme{CambridgeUS}
\usecolortheme{dolphin}
}
\setbeamertemplate{button}{\tikz
  \node[
  inner xsep=10pt,
  draw=structure!80,
  fill=structure!50,
  rounded corners=4pt]  {\Large\insertbuttontext};}

\setbeamertemplate{section page}
{
    \begin{centering}
    \begin{beamercolorbox}[sep=12pt,center]{part title}
    \usebeamerfont{section title}\insertsection\par
    \end{beamercolorbox}
    \end{centering}
}

\title{Clark and Martorell (2014)}

\begin{document}
\maketitle
\begin{frame}[<+->]{How I Read a Paper}
\begin{itemize}
\item Questions:
	\begin{itemize}
	\item What is the big picture question it's trying to get at?
	\item What is the specific question it's answering? \\~\\
	\end{itemize}
\item Approach:
	\begin{itemize}
	\item What's the ideal variation to answer the question?
	\item What is the actual variation used to answer the question?
	\item Suppose there's no actual effect: would the estimated effect be zero? \\~\\
	\end{itemize}
\item Findings:
	\begin{itemize}
	\item Do I \emph{really} believe the results?
	\item What else could have been have done to help convince me?
	\item If you're suddenly President (or CEO) for a day, does it change any of your decisions?
	\end{itemize}
\end{itemize}
\end{frame}

\begin{frame}[<+->]{Clark and Martorell (2014)}
\begin{itemize}
\item They ask whether there is a signaling value to receiving a high school diploma in Texas from 1993-1997.
\item They use a regression discontinuity approach. Compare those right below the cut-off on a high school exam to those right above.
\item Pros:
	\begin{itemize}
	\item Well done empirically. I trust their empirical findings.
	\item Did a good job discussing the results, ruling out potential stories, and placing the results in context.
	\end{itemize}
\item Cons:
	\begin{itemize}
	\item Only 5\% of high school students in Texas. Although these are the individuals that you'd think might need signaling.
	\item I find the signaling vs. human capital debate in its narrowest sense ``academic." Doesn't change any of my policy beliefs.
	\end{itemize}
\end{itemize}
\end{frame}

\end{document}